For Finitary Induction-Induction, \\ Induction is Enough

### 2020-05-03 paper/paper.tex
abstract

\begin{abstract}
  xxx: rewrite. Inductive-inductive types (IITs) are a generalisation of inductive types in
  type theory. They allow the mutual definition of types with multiple sorts
  where later sorts can be indexed by previous ones. An example is the
  Chapman-style syntax of type theory with conversion relations for each sort
  where e.g.\ the sort of types is indexed by contexts. It follows from previous
  work by Altenkirch, Kaposi, and Kov{\'a}cs, that all finitary IITs can be constructed from a quotient
  inductive-inductive type (QIIT), namely the theory of IIT signatures. This is
  a small domain-specific type theory where a context is a signature for an
  IIT. In this paper we construct the theory of IIT signatures using only inductive types,
  thereby showing a reduction of all finitary IITs to inductive types.  We rely
  on function extensionality and uniqueness of identity proofs. We formalised
  the construction of the theory of IIT signatures in Agda.
\end{abstract}

>>>>

\begin{abstract}
  Inductive-inductive types (IITs) are a generalisation of inductive
  types in type theory. They allow the mutual definition of types with
  multiple sorts where later sorts can be indexed by previous ones. An
  example is the Chapman-style syntax of type theory with conversion
  relations for each sort where e.g.\ the sort of types is indexed by
  contexts. In this paper we show that if a model of extensional type
  theory (ETT) supports indexed W-types, then it supports finitely
  branching IITs. We use a small internal type theory called the
  theory of signatures to specify signatures for IITs. We show that if
  a model of ETT supports the syntax for the theory of signatures,
  then it supports all IITs. We construct this syntax from indexed
  W-types using preterms and typing relations and prove its initiality
  following Streicher. The construction of the syntax and its
  initiality proof were formalised in Agda.
\end{abstract}
